A performance comparison of Dask and Apache Spark for data-intensive neuroimaging pipelines

### 2019-07-30 latex/paper.tex
Final edits

For each run, we measured the application makespan as well as the cumulative 
data read, compute, data write, and engine overhead times across all application
tasks. 
The overhead calculation for each CPU is the end time of its last processed task
minus its runtime. The summation of those results is the
total overhead.

@@

\begin{figure}[!b]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/spark-inc-baseline.html}{
            \includegraphics[clip,width=\columnwidth,
            height=0.15\textheight]{images/spark_inc_gantt.png}}
        \caption{Spark}\label{fig:inc_spark_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-bag-inc-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/bag_inc_gantt.png}}
        \caption{Dask Bag}\label{fig:inc_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-delayed-inc-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/delayed_inc_gantt.png}}
        \caption{Dask Delayed}\label{fig:inc_dask_delayed_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-futures-inc-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/futures_inc_gantt.png}}
        \caption{Dask Futures}\label{fig:inc_dask_futures_gantt}
    \end{subfigure}
    \caption{Incrementation: 125 blocks, 10 iterations, \SI{4}{\second} delay, 8 workers,
8 CPUs/worker}\label{fig:inc_gantt}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/spark-histo-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/spark_histo_gantt.png}}
        \caption{Spark}\label{fig:histo_spark_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-bag-histo-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/bag_histo_gantt.png}}
        \caption{Dask Bag}\label{fig:histo_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-delayed-histo-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/delayed_histo_gantt.png}}
        \caption{Dask Delayed}\label{fig:histo_dask_delayed_gantt}
    \end{subfigure}
    \caption{Histogram (Python): 125 blocks, 8 workers, 8
    CPUs/worker}\label{fig:histo_gantt}
\end{figure}

@@

\begin{figure}[!tb]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/spark-histo_np-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/spark_histo_np_gantt.png}}
        \caption{Spark}\label{fig:histo_np_spark_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-bag-histo_np-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/bag_histo_np_gantt.png}}
        \caption{Dask Bag}\label{fig:histo_np_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-delayed-histo_np-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/delayed_histo_np_gantt.png}}
        \caption{Dask Delayed}\label{fig:histo_np_dask_delayed_gantt}
    \end{subfigure}
    \caption{Histogram (NumPy): 125 blocks, 8 workers, 8
    CPUs/worker}\label{fig:histo_np_gantt}
\end{figure}

@@

\begin{figure}[!htb]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/spark-bids-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/spark_bids_gantt.png}}
        \caption{Spark}\label{fig:bids_spark_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-bag-bids-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/bag_bids_gantt.png}}
        \caption{Dask Bag}\label{fig:bids_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-delayed-bids-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/delayed_bids_gantt.png}}
        \caption{Dask Delayed}\label{fig:bids_dask_delayed_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-futures-bids-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/futures_bids_gantt.png}}
        \caption{Dask Futures}\label{fig:bids_dask_futures_gantt}
    \end{subfigure}
    \caption{BIDS App example: 8 workers}\label{fig:bids_gantt}
\end{figure}

@@

Overall, our experiments did not show any substantial performance
difference between Spark and Dask. In contradiction to the experiments
of~\cite{Mehta:17}, we did not observe consequential overhead differences
due to serialization or startup costs. This apparent contradiction is most
likely coming from differences in applications, engine parametrizations, or
infrastructure characteristics. In our case, potential overhead differences were
compensated by reverse trends in data transfer time. Since our focus is
Big Data applications, this leads us to conclude that engines are
equivalent.

>>>>

For each run, we measured the application makespan as well as the cumulative 
data read, compute, data write, and engine overhead times across all application
tasks. 
The overhead calculation for each CPU is the end time of its last processed task
minus the total runtime of the tasks it executed. The summation of those results is the
total overhead.

@@

\begin{figure}[!b]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/spark-inc-baseline.html}{
            \includegraphics[clip,width=\columnwidth,
            height=0.15\textheight]{images/spark_inc_gantt.png}}
        \caption{Spark}\label{fig:inc_spark_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-bag-inc-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/bag_inc_gantt.png}}
        \caption{Dask Bag}\label{fig:inc_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-delayed-inc-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/delayed_inc_gantt.png}}
        \caption{Dask Delayed}\label{fig:inc_dask_delayed_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-futures-inc-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/futures_inc_gantt.png}}
        \caption{Dask Futures}\label{fig:inc_dask_futures_gantt}
    \end{subfigure}
    \caption{Incrementation Gantt chart: 125 blocks, 10 iterations, \SI{4}{\second} delay, 8 workers,
8 CPUs/worker. All Gantt charts are clickable and link to interactive figures with additional information.}\label{fig:inc_gantt}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/spark-histo-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/spark_histo_gantt.png}}
        \caption{Spark}\label{fig:histo_spark_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-bag-histo-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/bag_histo_gantt.png}}
        \caption{Dask Bag}\label{fig:histo_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-delayed-histo-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/delayed_histo_gantt.png}}
        \caption{Dask Delayed}\label{fig:histo_dask_delayed_gantt}
    \end{subfigure}
    \caption{Histogram (Python) Gantt chart: 125 blocks, 8 workers, 8
    CPUs/worker}\label{fig:histo_gantt}
\end{figure}

@@

\begin{figure}[!tb]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/spark-histo_np-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/spark_histo_np_gantt.png}}
        \caption{Spark}\label{fig:histo_np_spark_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-bag-histo_np-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/bag_histo_np_gantt.png}}
        \caption{Dask Bag}\label{fig:histo_np_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-delayed-histo_np-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/delayed_histo_np_gantt.png}}
        \caption{Dask Delayed}\label{fig:histo_np_dask_delayed_gantt}
    \end{subfigure}
    \caption{Histogram (NumPy) Gantt chart: 125 blocks, 8 workers, 8
    CPUs/worker}\label{fig:histo_np_gantt}
\end{figure}

@@

\begin{figure}[!htb]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/spark-bids-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/spark_bids_gantt.png}}
        \caption{Spark}\label{fig:bids_spark_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-bag-bids-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/bag_bids_gantt.png}}
        \caption{Dask Bag}\label{fig:bids_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-delayed-bids-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/delayed_bids_gantt.png}}
        \caption{Dask Delayed}\label{fig:bids_dask_delayed_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-futures-bids-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/futures_bids_gantt.png}}
        \caption{Dask Futures}\label{fig:bids_dask_futures_gantt}
    \end{subfigure}
    \caption{BIDS App example Gantt chart: 8 workers}\label{fig:bids_gantt}
\end{figure}

@@

Overall, our experiments did not show any substantial performance
difference between Spark and Dask. In contradiction with the experiments
of~\cite{Mehta:17}, we did not observe consequential overhead differences
due to serialization or startup costs. This apparent contradiction is most
likely coming from differences in applications, engine parametrization, or
infrastructure characteristics between the two studies. In our case, potential overhead differences were
compensated by reverse trends in data transfer time. Since our focus is
Big Data applications, this leads us to conclude that engines are
equivalent.
